---
title: "Preparing Data with mlr3"
author: "Hans W. Borchers"
date: "July 2020"
output:
  html_document:
    css: "mlr3.css"
    keep_md: true
    toc: true
    toc_float:
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE}
library(mlr3verse, quietly = TRUE)
```


## The Task and the Data

Again we define our data and task as 
```{r}
Glass <- RWeka::read.arff("glass.arff")
mytask <- TaskClassif$new(id = "glass",
                          backend = Glass, target = "Type")
```

'mlr3' allows for inspecting, changing, and visualizing the task and especially the data through commands.
```{r}
mytask$nrow; mytask$ncol  # dim(Glass)
mytask$feature_names; mytask$target_names
```

We can display the data or a part of it,
```{r}
mytask$data()  # rows=c(1:10); cols=c("Type", "Al", "Ba")
```

or show a summary of the data.
```{r}
summary(as.data.table(mytask))
```


## Selecting and Filtering

We can select (or filter) the data, even with the intention to define a new task to work on. But be carefull: These operations will change the data internally, therefore before doing so we will copy the task object.
```{r}
mytask_copy <- mytask$clone()

mytask$select(c("Al", "Ba"))  # "Type" not possible
mytask

mytask$filter(c(1:5))
mytask
```

Note that this changes the original task (in place?), as can be seen from the much reduced sizes.

We can also look at the 'backend' (of the original data).
```{r}
mytask_copy$backend
```

We can also extend the data with the `cbind` and `rbind` methods, adding columns or rows to it.

Selecting or filtering will not copy the data, not even internally. Instead the ste of current indices for valid rows and columns is manipulated.


## Plotting Data and Tasks

There are several plotting functions associated with 'mlr3', the simplest one is `autoplot`. We plot the copy from above to get a picture of the full set.
```{r}
autoplot(mytask_copy)
```

